Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web

### 2024-11-26 autovi_paper.qmd
Comment -- Patrick needs to address
Some streamlining/rephrasing.

This distance measure requires knowledge of the true residual distribution, which is typically unknown. Therefore, a computer vision model was used for estimating the residual distribution [see @li2024automated for more details].

@@

The main purpose of `autovi` is to provide rejection decisions and $p$-values for testing the null hypothesis ($H_0$) that the regression model is correctly specified. The package provides automated interpretation of residual plots using computer vision. The name `autovi` stands for **auto**mated **v**isual **i**nference. <!--While initially designed for linear regression residual diagnostics, it has the potential to be extended to broader visual inference applications, as we discuss in section @sec-autovi-infrastructure.-->

There are two ways to access the package, directly using R or through a web interface, `autovi.web`. The web interface has the advantage that it can be used without installing Python, R and the relevant packages locally.

## Motivation for usage {#sec-why}

>>>>

This distance measure requires knowledge of the true residual distribution, which is typically unknown. Therefore, a computer vision model was used for estimating the residual distribution [see @li2024automated for more details].
XXX this isn't completely clear -- why is the computer vision model used to estimate the residual distribution?  You need to provide at least a bit of the "why" so that this isn't a total non-sequitur. XXX

@@

The main purpose of `autovi` is to provide rejection decisions and $p$-values for testing the null hypothesis ($H_0$) that the regression model is correctly specified. The package provides automated interpretation of residual plots using computer vision. The name `autovi` stands for **auto**mated **v**isual **i**nference. <!--While initially designed for linear regression residual diagnostics, it has the potential to be extended to broader visual inference applications, as we discuss in section @sec-autovi-infrastructure.-->
This functionality can be accessed through the R package `autovi`, or through a web interface, `autovi.web`, which allows use without the full installation of R, Python, and package dependencies on the user's system.  locally.

## Motivation {#sec-why}
